Modeling potential JCPOA diversion scenarios with Cyclus

### 2018-05-04 paper.tex
some rearanging

\section{The Experiment}
\subsection{The Fuel Cycle}
This work aims to assess the impact of the functional uncertainties of a
simple transition (see Figure \ref{fig:cycle}) inspired from the EG23 of the Screening And
Evaluation Group\cite{FCO}: a transition from light water reactors fleet loaded
with \glspl{UOX} fuel to a sodium fast reactors fleet loaded \glspl{MOX} fuel, considering an
$1\%/$y grows of the generated power (Figure \ref{fig:power}).
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.31]{cycle.png}
  \caption{Illustration of the material flow between the different facilities,
  with in green each operational parameters associated with an
  uncertainty.}\label{fig:cycle}
\end{figure}

As illustrated on Figure \ref{fig:power}, the transition starts with a fleet
fully composed by \glspl{LWR} loaded with enriched \glspl{UOX} fuel. The actual
transition starts around year 35, with the deployment of \glspl{FBR}, loaded
with Mixed oxide fuel (MOX), consisting of plutonium blended with natural
uranium. Once the transition to a full \glspl{FBR} fleet is completed, the
\glspl{FBR} fleet is slowly replaced with \glspl{FBR} with a lower breeding
ratio.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.32]{power.png}
    \caption{Electric power generated over time, with in blue the full production,
        in orange the \glspl{LWR} contribution, in green the hight breeding ratio
        \glspl{FBR} and in red the low breeding ratio \glspl{FBR}.}\label{fig:power}
\end{figure}

@@

\subsection{Uncertainty Measurements}
In this specific study, one will only focus on the uncertainty on the produced
electric power as a function of time, on the total quantity of natural uranium
used and on the total unused fissile inventory (unused reprocessed plutonium).
In order to estimate the total uncertainty on those 3 parameters as well as the
individual contribution of the operational parameters several set of (199)
simulations have been completed.  All uncertainty are computed as the standard
deviation over over all the calculations in the set.

@@

\subsection{Generated Power}
By construction, the very low uncertainty (Figure \ref{fig:power_full}) on the
generated power is expected.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.35]{power_full}
    \caption{Electric power generated as a function of time. The black line
        represents the reference calculation and the blue zone
        represents the 1 $\sigma$ uncertainty distribution.}\label{fig:power_full}
\end{figure}

@@

\section{Discussion}

>>>>

\section{The Experiment}
\subsection{The Fuel Cycle}
This work estimates the impact of the operationnal parameters uncertainty on a simple
transition (see Figure \ref{fig:cycle}) inspired from the EG23 of the Screening
And Evaluation Group\cite{FCO}: a transition from light water reactors fleet
loaded with \glspl{UOX} fuel to a sodium fast reactors fleet loaded \glspl{MOX}
fuel, considering an $1\%/$y grows of the generated power (Figure
\ref{fig:power}).

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.31]{cycle.png}
  \caption{Illustration of the material flow between the different facilities,
  with in green each operational parameters associated with an
  uncertainty.}\label{fig:cycle}
\end{figure}

As illustrated on Figure \ref{fig:power}, the transition starts with a fleet
fully composed by \glspl{LWR} loaded with enriched \glspl{UOX} fuel. The actual
transition starts around year 35, with the deployment of \glspl{FBR}, loaded
with Mixed oxide fuel (MOX), consisting of plutonium blended with natural
uranium.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.18]{power.png}
    \caption{Electric power generated over time, with in blue the full production,
        in orange the \glspl{LWR} contribution, in green the \glspl{FBR}.}\label{fig:power}
\end{figure}

@@

\section{Results}
In this specific study, one will only focus on the uncertainty on the produced
electric power as a function of time, on the total quantity of natural uranium
used and on the total unused fissile inventory (unused reprocessed plutonium).
In order to estimate the total uncertainty on those 3 parameters as well as the
individual contribution of the operational parameters several set of (199)
simulations have been completed.  All uncertainty are computed as the standard
deviation over over all the calculations in the set.

@@

\subsection{Generated Power}

\begin{figure}[h!] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.35]{power_full}
    \caption{Electric power generated as a function of time. The black line
        represents the reference calculation and the blue zone
        represents the 1 $\sigma$ uncertainty distribution.}\label{fig:power_full}
\end{figure}
By construction, the very low uncertainty (Figure \ref{fig:power_full}) on the
generated power is expected.

@@

\subsection{Discussion}
